Global optimization method with dual Lipschitz constant estimates for problems with non-convex constraints\thanks{This research was supported by the Russian Science Foundation, project No. 16-11-10150.}

### 2020-04-08 2019/NUMTA_Barkalov/SoftComputing/article.tex
Fix final reviewr's comments

\begin{abstract}
This paper considers the constrained global optimization problems, in which the functions are of the “black box” type and satisfy the Lipschitz condition. The algorithms for solving the problems of this class require the use of adequate estimates of the a priori unknown Lipschitz constants for the problem functions. A novel approach presented in this paper is based on a simultaneous use of two estimates of the Lipschitz constant: an overestimated and an underestimated one. The upper estimate provides the global convergence whereas the lower one reduces the number of trials necessary to find the global optimizer with the required accuracy. The considered algorithm for solving the constrained problems doesn’t use the ideas of the penalty function method; each constraint of the problem is accounted for separately. The convergence conditions of the proposed algorithm are formulated in the corresponding theorem. The results of the numerical experiments on a series of multiextremal problems with non-convex constraints demonstrating the efficiency of the proposed scheme of dual Lipschitz constant estimates are presented.
\keywords{Global optimization \and Multiextremal problems \and Non-convex constraints \and Lipschitz constant estimates \and Dimensionality reduction \and Numerical methods}
%\subclass{90C26}
\end{abstract}

@@

From Step 3 and Step 7 of the index algorithm, it follows that
\begin{equation}\label{max_gamma}
\max \{x_t-x^{k+1},x^{k+1}-x_{t-1}\} \leq \gamma (x_t-x_{t-1}),
\end{equation}
where $\gamma = \frac{r+1}{2r}<1$  and $ r=\min\{r_\nu:1\leq\nu\leq m+1\}>1$.
The contraction property (\ref{lim_delta_t}) and the property (\ref{nested_int}) for the product of all intervals (\ref{intervals_t}) are the consequences of (\ref{max_gamma}).

>>>>

\begin{abstract}
This paper considers the constrained global optimization problems, in which the functions are of the “black box” type and satisfy the Lipschitz condition. The algorithms for solving the problems of this class require the use of adequate estimates of the a priori unknown Lipschitz constants for the problem functions. A novel approach presented in this paper is based on a simultaneous use of two estimates of the Lipschitz constant: an overestimated and an underestimated one. The upper estimate provides the global convergence whereas the lower one reduces the number of trials necessary to find the global optimizer with the required accuracy. The considered algorithm for solving the constrained problems doesn't use the ideas of the penalty function method; each constraint of the problem is accounted for separately. The convergence conditions of the proposed algorithm are formulated in the corresponding theorem. The results of the numerical experiments on a series of multiextremal problems with non-convex constraints demonstrating the efficiency of the proposed scheme of dual Lipschitz constant estimates are presented.
\keywords{Global optimization \and Multiextremal problems \and Non-convex constraints \and Lipschitz constant estimates \and Dimensionality reduction \and Numerical methods}
%\subclass{90C26}
\end{abstract}

@@

From Step 3 and Step 7 of the index algorithm, it follows that
\begin{equation}\label{max_gamma}
\max \{x_t-x^{k+1},x^{k+1}-x_{t-1}\} \leq \gamma (x_t-x_{t-1}),
\end{equation}
where $\gamma = \frac{r+1}{2r}<1$  and $ r=\min\{r_\nu:1\leq\nu\leq m+1\}>1$.
The contraction property (\ref{lim_delta_t}) and the property (\ref{nested_int}) for the intersection of all intervals (\ref{intervals_t}) are the consequences of (\ref{max_gamma}).
